Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-18 docs/report/report.tex
updated report, added outline list

\section{Introduction}

The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference). However most of these methods usually assume that the landing zone is static and that there is very little wind or disturbances. In cases of high wind or a rapidly moving platform, which from the quadrotor's reference frame can be be though of as nearly equivalent cases, normal autonomous landing procedures will likely fail.

@@

In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions. The calibration file passed to the AprilTag library during the state estimation proccedure is selected based on what the current camera resolution is set at.

>>>>

\section{Layout for Report}
\begin{itemize}
	\item Introduction
	\item Related work
	\item Hardware
	\item Software libraries used
	\item Methods
	\begin{itemize}
		\item camera methods (image processing)
		\item PID controllers
	\end{itemize}
	\item Results and Discussion
	\begin{itemize}
		\item Image Processing Results
		\item PID Results and Testing
		\item Hardware difficulties? 
	\end{itemize}
	\item Future work 
	\item Conclusion
\end{itemize}

\section{Introduction}
The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference). However most of these methods usually assume that the landing zone is static and that there is very little wind or disturbances. In cases of high wind or a rapidly moving platform, which from the quadrotor's reference frame can be be though of as nearly equivalent cases, normal autonomous landing procedures will likely fail.

@@

In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions. The calibration file passed to the AprilTag library during the state estimation procedure is selected based on what the current camera resolution is set at.
